\textbf{QSOT} abbreviates \emph{Quantum State Over Time}. \texttt{QSOT2} is a
mathematical-consistency verifier for a phenomenological curved-spacetime quantum-channel
model: it maps the Frobenius norm of a background's Riemann tensor to a single-qubit
decoherence channel and checks that the resulting quantum-mechanical machinery is
internally consistent, deterministic, and reproducible.

\paragraph{Lineage.} The QSOT line passed through three forms. \emph{QSOT~v1} was an
intentional high-formality slop artifact, formal-looking but effectively non-running.
\emph{QSOT-Harness} was an honest reconstruction that made the model run and added an
epistemic-governance shell; it remains the published combined snapshot. \texttt{QSOT2}
re-scopes that work to its mathematical core --- the model and its verification harness
--- with the governance machinery deliberately lifted out so the verification is legible
on its own terms.

\paragraph{Retained scope.} QSOT2 verifies (i) internal quantum-mechanical consistency of
the implemented maps, (ii) deterministic execution of an end-to-end pipeline, and (iii)
reproducible numerical outputs. What it deliberately does \emph{not} claim is centralized
in \S\ref{sec:limits}.

\paragraph{Claim boundary.} A passing QSOT2 check certifies model-internal mathematical
consistency under stated assumptions \emph{only}. The curvature-to-channel mapping is a
phenomenological ansatz whose curvature inputs are non-derived toy values; the
admissibility-gate and verdict labels are implementation-defined classifications, not
physical observables. Accordingly the checks read as executable regression and
consistency tests, not as empirical support for the ansatz. The full non-claim list is
centralized in \S\ref{sec:limits}.
