Phase~0 verifies five temporal-state axioms of the implemented single-qubit channel maps.
Each is a falsifiable numerical predicate evaluated to machine precision; a check passes
when its deviation is below a fixed tolerance ($\texttt{atol}=\texttt{rtol}=10^{-9}$).
The axioms are standard consistency conditions for quantum channels and open-system
state evolution~\cite{Breuer2002}.

\begin{description}[leftmargin=1.5em]
\item[Linearity.] For a channel $\mathcal{E}$, states $\rho_a,\rho_b$, and scalars $p,q$,
  the quantity $\big\lVert \mathcal{E}(p\rho_a+q\rho_b) - p\,\mathcal{E}(\rho_a) -
  q\,\mathcal{E}(\rho_b)\big\rVert$ must vanish.
\item[CPTP completeness.] For Kraus operators $\{K_i\}$,
  $\big\lVert \sum_i K_i^\dagger K_i - I\big\rVert_F$ must vanish.
\item[Trace preservation.] For each test state,
  $\big|\operatorname{Tr}\mathcal{E}(\rho)-\operatorname{Tr}\rho\big|$ must vanish.
\item[Conditionability.] One- and two-step trajectory replays must match the composed
  channel prediction: $\rho_{i+1} \approx \mathcal{E}_i(\rho_i)$ and
  $\rho_{i+2}\approx \mathcal{E}_{i+1}(\mathcal{E}_i(\rho_i))$.
\item[Density validity.] Each evolved $\rho$ must be Hermitian, unit-trace, and positive
  semidefinite.
\end{description}

In the reference run the realized deviations sit at machine epsilon: linearity
$\sim 1.1\times10^{-16}$, CPTP completeness $\sim 1.6\times10^{-16}$, and trace
preservation $\sim 4.4\times10^{-16}$; the composed-channel, sequential-replay, and
two-step conditionability deviations are exactly $0$. These are reported as
machine-precision evidence, not as prose assurances. Because the channels are CPTP by
construction, these axiom checks function as executable regression and consistency tests:
they guard the implementation against drift and confirm the maps behave as specified, but
they are \emph{not} independent evidence that the underlying ansatz is physically correct.
That distinction is the point --- Phase~0 makes QSOT2 a verifier with falsifiable numerical
predicates rather than a narrative artifact.
