Phases~1--3 exercise the retained model pipeline outside the KD and memory-proxy
diagnostics.

\paragraph{Flat baselines (Phase~1).} A qubit evolved through a flat Minkowski
background, at rest and boosted, preserves purity ($P=1.0$) and zero von Neumann entropy
and clears the causal-structure gate. This fixes the no-noise limit of the implemented
map.

\paragraph{Curvature noise (Phase~2).} Across the curved backgrounds the channel map
$p = 1-\exp(-\alpha\lVert \mathrm{Riemann}\rVert_F)$ drives purity decay and entropy
growth. Here $\lVert \mathrm{Riemann}\rVert_F$ is the Frobenius norm of a \emph{non-derived}
curvature proxy --- hand-set toy constants for the Ricci-flat cases and a copy of the Ricci
matrix for the conformally curved cases (each background records its \texttt{riemann\_source}
and a boolean \texttt{riemann\_is\_toy} flag in the result artifact). The norm is therefore a
pure number, so $\alpha\lVert \mathrm{Riemann}\rVert_F$ is dimensionless by construction and
$\alpha$ is a dimensionless calibration multiplier, not a physical curvature scale. In the
reference run ($\alpha=0.1$): Schwarzschild $P=0.99943$, de~Sitter
$P=0.63607$, AdS5 $P=0.67764$, and Eguchi--Hanson $P=0.99887$, with von Neumann entropies
of $0.0026$, $0.5501$, $0.5031$, and $0.0048$ respectively. The design separates the two
curvature roles: the \emph{Riemann} norm drives decoherence --- so Ricci-flat vacua such
as Schwarzschild and Eguchi--Hanson still decohere through non-zero tidal curvature ---
while the \emph{Ricci}-based residual feeds the admissibility gate. The retained gate
pattern is \texttt{PASS} for flat/Schwarzschild/AdS5 and \texttt{FAIL} for de~Sitter
(non-zero beta residual), Eguchi--Hanson (gravitational-anomaly proxy), and G\"odel
(closed timelike curve). These are implementation-defined classifications, not physical
observables; each verify block serializes its decision as a machine-readable
\texttt{policy\_reason\_code} field (e.g.\ \texttt{nonzero\_beta\_residual},
\texttt{ctc\_failure}, \texttt{anomaly\_failure}).

\paragraph{Relativistic boosts (Phase~3).} A boost $\beta>0$ increases the effective
noise parameter through the combination of gravitational and kinematical time dilation,
in the intended direction. This section explains how the implemented model behaves, not
why nature must behave that way.
