Phase~4 reports a single bounded diagnostic and keeps its interpretation narrow.

\begin{enumerate}[leftmargin=1.5em]
\item The implementation searches single-qubit measurement-basis angles to minimize the
  real part of a Kirkwood-Dirac quasiprobability,
  $\min \operatorname{Re}\operatorname{Tr}(P_b P_a \rho)$, following the standard
  Kirkwood--Dirac quasiprobability construction~\cite{Kirkwood1933,Dirac1945}.
\item The flat and de~Sitter optima are reported separately: in the reference run
  $Q^{\text{flat}}_{\mathrm{KD}} \approx -0.1234$ and
  $Q^{\text{de Sitter}}_{\mathrm{KD}} \approx -4.7\times10^{-4}$.
\item The reported signal is the flat-relative difference
  $\Delta_{\mathrm{KD}} = Q^{\text{de Sitter}}_{\mathrm{KD}} - Q^{\text{flat}}_{\mathrm{KD}}
  \approx +0.1230$.
\item Convergence is reported independently of the value. Convergence here means the
  early-stop criterion fired: the objective failed to improve by more than $10^{-6}$ for
  $20$ consecutive steps. On the flat baseline the objective is still improving at the
  final step (its best value coincides with the last step), so within the fixed $50$-step
  budget the criterion never fires and convergence is recorded \texttt{false}; the
  de~Sitter search, by contrast, early-stops at step~$42$. Non-convergence here therefore
  means \emph{not yet plateaued}, not \emph{diverged}: the reported value is the best
  observed objective and is well defined regardless. The KD check is surfaced as
  \texttt{DEGRADED\_PASS} rather than hidden.
\end{enumerate}

Two rules bound the reading. First, negative KD in an optimized basis is a generic
property of single-qubit states; it is \emph{not} a curvature or contextuality proof.
Only the flat-relative delta is reported, and even that is a model-relative quantity.
Second, the reported value tracks the \emph{best} observed objective (best and last
values are recorded separately), not merely the final optimizer step. This section
therefore reads as a bounded diagnostic report, not a contextuality theorem. Phase~4 is a
\emph{diagnostic-tier} check: its convergence flag is the sole input to the single degraded
label and is reported separately from the Phase~0 consistency axioms, which it does not
affect (see the tiered reading in \S\ref{sec:results}).
