Table~\ref{tab:qsot2_results} consolidates the reference run ($\alpha=0.1$, six
backgrounds). The pipeline runs Phase~0 plus Phases~1--5 (35 deterministic checks) and
returns an overall \texttt{DEGRADED\_PASS}: 34 checks pass and one is degraded (the
flat-baseline KD non-convergence). There are no failures and no governance/audit phases.
Read by tier, all five Phase~0 consistency axioms and every Phase~1--3 model check pass;
the sole degraded entry is the diagnostic-tier KD convergence flag (\S\ref{sec:phase4}), so
all retained mathematical-consistency checks pass; the degraded label comes solely from
optimizer hygiene, not an axiom violation.

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}lcc@{}}
\toprule
Quantity & Value & Note \\
\midrule
Overall verdict & \texttt{DEGRADED\_PASS} & 34 pass / 0 fail / 0 skip / 1 degraded \\
Checks (total) & 35 & Phase 0 + Phases 1--5 \\
$P_{\mathrm{Schw}}/P_{\mathrm{dS}}/P_{\mathrm{AdS5}}/P_{\mathrm{EH}}$
  & $0.99943/0.63607/0.67764/0.99887$ & purity (Schw / dS / AdS5 / EH) \\
$S_{\mathrm{dS}}/S_{\mathrm{AdS5}}$ & $0.5501/0.5031$ & von Neumann entropy \\
$\Delta_{\mathrm{KD}}$ & $+0.1230$ & flat-relative, non-converged \\
$\mathrm{nm}$ (self-test / model) & $1.41\times10^{-4}\;/\;0$ & detector vs.\ model \\
axiom deviations & $\le 4.4\times10^{-16}$ & machine epsilon \\
\bottomrule
\end{tabular}
\caption{Consolidated QSOT2 reference-run outputs.}
\label{tab:qsot2_results}
\end{table}

\paragraph{Sensitivity.} A three-point $\alpha$ sweep (committed as
\texttt{reports/sweep\_alpha.json}, regenerated by \texttt{scripts/alpha\_sweep.py}) tests
direction and ceiling, \emph{not robustness}: the apparent plateau is a structural artifact
of the flat baseline being curvature-free ($\lVert\mathrm{Riemann}\rVert_F=0$), so its
channel is the identity and its KD value $Q^{\text{flat}}_{\mathrm{KD}}=-0.1234$ is
\emph{independent of} $\alpha$. Only de~Sitter responds to $\alpha$: as it decoheres toward
the maximally mixed state its KD optimum approaches $0$, so $\Delta_{\mathrm{KD}}$ rises
toward the fixed ceiling $\lvert Q^{\text{flat}}_{\mathrm{KD}}\rvert\approx 0.1234$ and is
all but saturated by $\alpha=1.0$. The measured values are
$\Delta_{\mathrm{KD}} = +0.0135,\ +0.1230,\ +0.1235$ at $\alpha\in\{0.01, 0.1, 1.0\}$,
with the model-trajectory memory result staying $0$ throughout; absolute magnitudes remain
calibration-dependent.

\paragraph{Parity.} Every retained mathematical quantity above reproduces the
QSOT-Harness r1 math engine numerically. QSOT2 differs only by design: the
governance/audit surfaces are absent and the result schema is leaner.
