\paragraph{Run the experiment.}
\begin{verbatim}
python run_experiment.py --config configs/experiment.yaml --out reports
\end{verbatim}

\paragraph{Run the tests.}
\begin{verbatim}
python -m pytest
\end{verbatim}
The suite has 50 tests behind a 90\% coverage gate; the current suite measures
$\sim$96\%.

\paragraph{Artifacts and schema.} The run writes \texttt{reports/result.json} and
\texttt{reports/report.md}. The result carries
\texttt{schema\_id = qsot2.math\_consistency.experiment\_result.v1} and a four-field
claim boundary; it contains no evidence-class, audit-context, or calibration blocks.
Some legacy field names remain in the serialized verification artifact for backward
compatibility with the QSOT-Harness result surface; in QSOT2 they function only as
implementation-defined classification metadata and are not interpreted as governance or
audit evidence.

\paragraph{Artifact traceability.} Table~\ref{tab:artifact_traceability} ties each
manuscript-facing claim surface to a concrete repository artifact. The stable public
release anchor for this paper line is QSOT2~v0.1.1, DOI
\href{https://doi.org/10.5281/zenodo.20763331}{10.5281/zenodo.20763331}; the hashes below
are canonical-LF SHA-256 values of the repository files named in the first column.

\begin{table}[t]
\centering
\scriptsize
\setlength{\tabcolsep}{3pt}
\begin{tabularx}{\textwidth}{@{}p{0.19\textwidth} p{0.27\textwidth} p{0.19\textwidth} X@{}}
\toprule
Artifact & Role in paper & Schema / version & Traceability anchor \\
\midrule
\path{reports/result.json} &
Reference-run verdict, 35 checks, claim boundary, and retained numerical outputs &
\path{qsot2.math_consistency.experiment_result.v1} &
SHA-256 \artifacthash{efca2228f177634f8f0f83b93eb5a7bc9246afe55cf707e780d2791b8a685bfc}; release DOI
\path{10.5281/zenodo.20763331} \\

\path{reports/sweep_alpha.json} &
Three-point $\alpha$ sensitivity sweep behind \S\ref{sec:results} &
\path{qsot2.math_consistency.alpha_sweep.v1} &
SHA-256 \artifacthash{8e547946e4b6d874ec58e23584977b07151571742be37d5e51da075d66bce7b6} \\

\path{configs/experiment.yaml} &
Fixed reference-run configuration used by \path{run_experiment.py} &
\path{version: 0.1.1} &
SHA-256 \artifacthash{c3a28b59044b6fdba474ccfd08da0f38e376285dc84a2f69637cf1c99c2e7f51} \\

\path{pyproject.toml} &
Environment and dependency contract for the published package line &
\path{project.version = 0.1.1} &
SHA-256 \artifacthash{d73f4616a33618093f3ffd51225c8214dc887296a93fac831e9a4959cb119dab} \\

\path{tests/} &
Executable verification suite covering the retained math line &
50 tests; coverage gate $\geq 90\%$ &
Repository test surface for the v0.1.1 line; current suite measures $\sim$96\% \\
\bottomrule
\end{tabularx}
\caption{Artifact traceability for the QSOT2 paper line.}
\label{tab:artifact_traceability}
\end{table}

\paragraph{Alpha sweep.} The sensitivity sweep of \S\ref{sec:results} is reproduced by
\begin{verbatim}
python scripts/alpha_sweep.py
\end{verbatim}
which writes \texttt{reports/sweep\_alpha.json}
(\texttt{schema\_id = qsot2.math\_consistency.alpha\_sweep.v1}) without overwriting the
frozen reference \texttt{reports/result.json}.

\paragraph{Parity targets.} Against the QSOT-Harness r1 math engine the retained
quantities reproduce: $Q^{\text{flat}}_{\mathrm{KD}} \approx -0.1234$,
$Q^{\text{de Sitter}}_{\mathrm{KD}} \approx -4.7\times10^{-4}$,
$\Delta_{\mathrm{KD}} \approx +0.1230$, self-test $\mathrm{nm}\approx 1.41\times10^{-4}$,
model $\mathrm{nm}=0$, purities $0.99943/0.63607/0.67764/0.99887$, and axiom deviations at
machine epsilon. Re-runs are content-stable except for the \texttt{generated\_at}
timestamp.
